Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2024-01-24 README.Rmd
fix git url issue in README

# Print milestones
glue_data(milestones, "  - **[{time}]({link_to_git}): {description}**
        - **Milestone:** {name}
        - **Data MD5 hash**: {hash}
        - [Link to code snippet](https://https://github.com/StefanVermeent/liss_wm_profiles_2023/tree/main/.projectlog/{commit}.R)
        \n
    ")

>>>>

branch <- gert::git_branch_list() |> filter(local == TRUE) |> pull(name)

# Print milestones
glue_data(milestones, "  - **[{time}]({link_to_git}): {description}**
        - **Milestone:** {name}
        - **Data MD5 hash**: {hash}
        - [Link to code snippet](https://https://github.com/StefanVermeent/liss_wm_profiles_2023/blob/{branch}/.projectlog/{commit}.R)
        \n
    ")
